Supplement to: Optimal management of a stochastically varying population when policy adjustment is costly

### 2015-05-03 manuscripts/manuscript.Rmd
tidy and update documentation

Taken together this objective function \eqref{eq:objective} and the state
equation \eqref{eq:state_equation} define a stochastic dynamic programming
problem that we solve using backwards recursion via Bellman's equation.
We denote the resulting state-dependent, optimal control as $\mathbf{h}_0^{\ast}$.
We solve this problem on a finite time horizon of $T =$ `r OptTime` using
value iteration [@Mangel1988; @Clark2000]. (Longer horizon times have no
qualitative difference but stretch the plots making it more difficult
to visualize the fluctuations.)

R code for implementing the dynamic programming algorithm in this context is
provided as a supplementary R package to the paper. Scripts for replicating 
all of the analysis presented here are also provided in the Supplementary Material.

@@

ggplot(fees, aes(c2, (npv0-value)/npv0, lty=variable, color=variable)) + 
  geom_line() + 
  geom_hline(aes(yintercept=reduction), linetype=4) + 
  xlab("Penalty coefficient") +
  ylab("Reduction in net present value") + 
  scale_linetype_discrete(labels=relabel, breaks = c('L1', 'L2', 'fixed'), name = 'cost model') + 
  scale_color_discrete(labels=relabel, breaks = c('L1', 'L2', 'fixed'), name = 'cost model') 
 # rename scale from 'variable' to 'adjustment cost for policy:'

write.csv(dt, "components/data/100reps.csv")
write.csv(fees, "components/data/figure2.csv")

@@

fig5_dat <- hist_dat %>% 
  filter(penalty_fn=="L1") %>%
  select(-penalty_fn) %>%
  unite(dist, Assumption, variable, sep = " : ")
labels <- c(expression(paste("Costs under ",  Pi[1])), 
            expression(paste("Revenue under ", Pi[1])),
            expression(paste("Cost under ", Pi[0])), 
            expression(paste("Revenue under ", Pi[0])))
ggplot(fig5_dat) + 
  geom_density(aes(value, fill=dist, color=dist, lty=dist), alpha=0.5, size=1) +
  scale_fill_discrete(name="", labels=labels) + 
  scale_color_discrete(labels=labels, name="") + 
   scale_linetype_discrete(labels=labels, name="") +
  xlab("Realized NPV")

>>>>

Taken together this objective function \eqref{eq:objective} and the state
equation \eqref{eq:state_equation} define a stochastic dynamic programming
problem that we solve using backwards recursion via Bellman's equation.
We denote the resulting state-dependent, optimal control as $\mathbf{h}_0^{\ast}$.
We solve this problem on a finite time horizon of $T =$ `r OptTime` using
value iteration [@Mangel1988; @Clark2000].

R code for implementing the dynamic programming algorithm in this context is
provided as a supplementary R package to the paper, along with scripts for replicating 
the analyses presented here. To address concerns about computational reproducibility [@Boettiger2015],
a Docker container image of the software environment is also provided.

@@

ggplot(fees, aes(c2, (npv0-value)/npv0, lty=variable, color=variable)) + 
  geom_line() + 
  geom_hline(aes(yintercept=reduction), linetype=4) + 
  xlab("Penalty coefficient") +
  ylab("Reduction in net present value") + 
  scale_linetype_discrete(labels=relabel, breaks = c('L1', 'L2', 'fixed'), name = 'cost model') + 
  scale_color_discrete(labels=relabel, breaks = c('L1', 'L2', 'fixed'), name = 'cost model') + 
  annotate("text", mean(c2), reduction+.01, label = "Calibration for 25% reduction in NPV")
 # rename scale from 'variable' to 'adjustment cost for policy:'

write.csv(fees, "components/data/figure2.csv")

@@

fig5_dat <- hist_dat %>% 
  filter(penalty_fn=="L1") %>%
  select(-penalty_fn) %>%
  unite(dist, Assumption, variable, sep = " : ")
labels <- c(expression(paste("Costs under ",  Pi[1])), 
            expression(paste("Revenue under ", Pi[1])),
            expression(paste("Cost under ", Pi[0])), 
            expression(paste("Revenue under ", Pi[0])))
ggplot(fig5_dat) + 
  geom_density(aes(value, fill=dist, color=dist, lty=dist), alpha=0.5, size=1) +
  scale_fill_discrete(name="", labels=labels) + 
  scale_color_discrete(labels=labels, name="") + 
   scale_linetype_discrete(labels=labels, name="") +
  xlab("Realized NPV") + 
  ylab("Probability density of revenue/cost")

### 2015-05-03 manuscripts/supplement.Rmd
tidy and update documentation

>>>>

## Code and data for methods and analysis ##

All code and data used in this analysis can be found under the project's GitHub repository: [https://github.com/cboettig/pdg_control](https://github.com/cboettig/pdg_control). A snapshot of this repository representing the precise versions of the code used in this analysis has been permanently archived in the scientific software and data repository Zenodo, managed by CERN; and should be referenced or cited using its assigned digital object identifer, doi:xxx.  (This DOI is also clearly linked from the GitHub repository).

### Organization of code

The project repository is organized as an R package.  The intent is not to provide a general-purpose software tool for this kind of analysis, but rather to rely on a standardized directory structure for representing complex projects. It is our hope that this facilates understanding, reproducibility, and further exploration of these results sensu [Gentleman & Temple Lang 2007](http://biostats.bepress.com/bioconductor/paper2/), but caution that additional software engineering would be required before any of this could be applied in a different context.  The functions provided are largely specific to the analyses presented here and may undocumented or incompletely documented.

The source documents for both the manuscript and supplement are also found in the code repository using the dynamic document `.Rmd` format which embeds all of the code required for the analysis; see [http://rmarkdown.rstudio.com/](http://rmarkdown.rstudio.com/).

Within the `.Rmd` files themselves are found only the blocks of code required to generate each of the figures shown in the manuscript.  The analysis is sourced in from an external R script, `analysis.R` by a code block at the beginning of the `.Rmd` file.  This script in turn relies on more modular functions defined in the `R/` directory that define the stochastic dynamic programming optimization algorithms, simulation routines, and so forth.

### Data

All empirical or simulated data shown in the figures can also be found as tabular .csv files in this repository.

### Dependencies and machine images
